Alex's Notes and Text Fragments for the JSS Manuscript

### 2023-12-24 paper/article.Rmd
align figure sizes (points, axes, width)

```{r coords-eval, fig.cap='Leave-one-block-out CV based on $k$-means clustering of the coordinates as implemented in package \\pkg{sperrorest} (method `"spcv\\_coords"` in \\pkg{mlr3spatiotempcv}).', out.width="40%", fig.pos="ht", echo=FALSE}
rsmp_coords = rsmp("spcv_coords", folds = 5)

autoplot(rsmp_coords,
  size = 0.8, fold_id = 1, task = task) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

```{r vis-nspcv-non-eval, eval=FALSE}
autoplot(rsmp_nsp, task, fold_id = 1:2, size = 0.8)
```

```{r vis-nspcv-eval, fig.cap="Random (non-spatial) four-fold CV partitioning. Only the first two folds of the first repetition are shown.", fig.pos="ht", fig.height=6, fig.width=8, echo=FALSE}
autoplot(rsmp_nsp, task, fold_id = 1:2, size = 0.8) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

```{r vis-spcv-non-eval, eval=FALSE}
autoplot(rsmp_sp, task, fold_id = 1:2, size = 0.8)
```

```{r vis-spcv-eval, fig.cap="Spatial leave-one-block-out partitioning using coordinate-based clustering to create roughly equally sized polygonal blocks. Due to space limitations only the first two folds of the first repetition are shown.", fig.pos="ht", fig.height=6, fig.width=8, echo=FALSE}
autoplot(rsmp_sp, task, fold_id = 1:2, size = 0.8) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

>>>>

```{r knndm-eval, fig.cap='Leave-one-block-out CV based on $k$-means clustering of the coordinates as implemented in package \\pkg{sperrorest} (method `"spcv\\_coords"` in \\pkg{mlr3spatiotempcv}).', out.width="55%", fig.pos="ht", echo=FALSE}
rsmp_coords = rsmp("spcv_coords", folds = 5)

@@

```{r vis-nspcv-non-eval, eval=FALSE}
autoplot(rsmp_nsp, task, fold_id = 1:2, size = 0.3)
```

```{r vis-nspcv-eval, fig.cap="Random (non-spatial) four-fold CV partitioning. Only the first two folds of the first repetition are shown.", out.width="100%", fig.pos="ht", echo=FALSE}
autoplot(rsmp_nsp, task, fold_id = 1:2, size = 0.3) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.02)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.02)) *
  ggplot2::theme(plot.title = ggtext::element_textbox(size = 8),
    axis.text = ggplot2::element_text(size = 8)) *
  ggplot2::guides(colour = ggplot2::guide_legend(override.aes = list(size = 0.8)))
```

```{r vis-spcv-non-eval, eval=FALSE}
autoplot(rsmp_sp, task, fold_id = 1:2, size = 0.3)
```

```{r vis-spcv-eval, fig.cap="Spatial leave-one-block-out partitioning using coordinate-based clustering to create roughly equally sized polygonal blocks. Only the first two folds of the first repetition are shown.", fig.pos="ht", out.width="100%", echo=FALSE}
autoplot(rsmp_sp, task, fold_id = 1:2, size = 0.3) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.02)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.02)) *
  ggplot2::theme(plot.title = ggtext::element_textbox(size = 8),
    axis.text = ggplot2::element_text(size = 8)) *
  ggplot2::guides(colour = ggplot2::guide_legend(override.aes = list(size = 0.8)))
```
